Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-25 analysis/paper/paper.Rmd
Update to results section, was unable to change the labels on the bar charts to human-meaningful values; added a small table with said human-meaningful values just for now

<!-- BM: Need to add citations and definition about univariate k-means -->

<!-- QH: added more info on univariate k-means, as well as a citation  -->

@@

```{r}
# let's look at all the PCs and how much each original # variable contributes to them

@@

plot_grid(PC1_contrib, 
          PC2_contrib)

@@

>>>>

@@

```{r contribution_plots}
# let's look at all the PCs and how much each original # variable contributes to them

@@

# This is a temporary fix just to get the labels looking nice for now; there is most certainly a cleaner way to do this
# My fix did not work. I will have to create a temp table showing the values for now

# PC1_contrib[["plot_env"]][["xx"]] <- as.factor(c("X Value: Top Left",
#                                              "Y Value: Top Left",
#                                               "Y Value: Mid-Upper Left",
#                                               "X Value: Mid-Lower Left",
#                                               "Y Value: Mid-Lower Left",
#                                               "X Value: Bottom Left",
#                                               "Y Value: Bottom Left",
#                                               "X Value: Distal Tip",
#                                               "Y Value: Distal Tip",
#                                               "X Value: Bottom Right",
#                                               "Y Value: Bottom Right",
#                                               "X Value: Mid-Lower Right",
#                                               "Y Value: Mid-Lower Right",
#                                               "X Value: Mid-Upper Right",
#                                               "Y Value: Mid-Upper Right",
#                                               "X Value: Top Right",
#                                               "Y Value: Top Right"))
#

#iris$Species[iris$Species == 'virginica'] <- 'setosa'

#PC1_contrib[["plot_env"]][["data"]][["name"]][PC1_contrib[["plot_env"]][["data"]][["name"]] == '5.X'] <- "X Value: Distal Tip"

#PC1_contrib[["plot_env"]][["data_sum"]][["name"]] <- as.factor(c(1:18))

output_meanings <-tibble(data.frame(c("X Value: Top Left",
         "Y Value: Top Left",
         "X Value: Mid-Upper Left",
         "Y Value: Mid-Upper Left",
         "X Value: Mid-Lower Left",
         "Y Value: Mid-Lower Left",
         "X Value: Bottom Left",
         "Y Value: Bottom Left",
         "X Value: Distal Tip",
         "Y Value: Distal Tip",
         "X Value: Bottom Right",
         "Y Value: Bottom Right",
         "X Value: Mid-Lower Right",
         "Y Value: Mid-Lower Right",
         "X Value: Mid-Upper Right",
         "Y Value: Mid-Upper Right",
         "X Value: Top Right",
         "Y Value: Top Right"),
       c("1X",
         "1Y",
         "2X",
         "2Y",
         "3X",
         "3Y",
         "4X",
         "4Y",
         "5X",
         "5Y",
         "6X",
         "6Y",
         "7X",
         "7Y",
         "8X",
         "8Y",
         "9X",
         "9Y")))

output_meanings <- setNames(output_meanings, c("Landmark Value", "Computer Output"))

plot_grid(PC1_contrib, 
          PC2_contrib)
 output_meanings

@@

  <!-- Could not figure out how to change the labels on the x axis for the two bar charts, so I included a small table with the human-meaningful values for now-->
